### 2013-11-13 manuscripts/reply/reply-main.tex
Working on reply manuscript.
Making miscellaneous edits throughout, starting to move some of the text
to a Supporting Info (SI) section. Adding files which will contain SI
text (`reply-si-main.tex`) and SI figures (`reply-si-figures.tex`).

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They mention how the use of uniform prior distributions in \msb for many of the
model's parameters necessitates awkward broad priors to avoid excluding the
truth, \textit{a priori}.
What \citet{Hickerson2013} mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  
\citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

@@

%CWL:This should be in the section on model-averaging, not empirical Bayes
%limitations
We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a marginal posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

%CWL: This seems to specific, not sure about including
\section*{Validation analyses}
% \highLight{Not sure where to put this section}.
% \highLight{This justifies presenting the unadjusted results in this paper.}
% \highLight{Is it worth including just for this purpose?}
Following \citet{Oaks2012}, we characterize the model-choice behavior of the
model-averaging approach of \citet{Hickerson2013} under the ideal conditions
where the prior is correct (i.e., the data are generated from parameters drawn
from the same prior distributions used in the analysis).
We used the same prior models as above ($M_1$--$M_5$;
Table~\ref{tabModelChoiceEmpirical}), and generated 50,000 pseudo-replicate
datasets under this prior (10,000 from each model).
We used a simulated data structure of eight population pairs, with a single
1000 base-pair locus sampled from 10 individuals from each population.
We then analyzed each of these replicate datasets using the same prior,
retaining 1000 posterior samples.
Our results are very similar to \citet{Oaks2012}, but we note that they
are not directly comparable as our simulations contained eight population
pairs rather than 10 (Figure~\ref{figValidationMCBehavior}).
We find that the approach of \citet{Hickerson2013} estimates the posterior
probability of divergence models reasonably well when all assumptions of the
method are met (i.e., the prior is correct) and the unadjusted posterior
estimates are used.
Similar to \cite{Oaks2012}, we find that the regression-adjusted estimates of
the model probabilities are biased.

@@

\subsection*{Graphical checks of priors}
\citet{Hickerson2013} advocate the use of what they call graphical checks of
prior models.
This entails generating a small number of random samples from the prior (1000)
and plotting the resulting summary statistics in comparison to the observed
statistics to see if they coincide (see Figure 1 of \citet{Hickerson2013}).
As we show above, this is a risky strategy, because the resulting plots of this
approach have little correlation with the appropriateness of priors.
Given the richness of the \msb model ($\approx 600$ parameters for the Philippine
dataset analyzed by \citet{Hickerson2013}), we do not expect that 1000
\emph{random} draws from the vast prior parameter space will yield data and
summary statistics consistent with the observed data.
In fact, when the random draws are tightly clustered around the observed
statistics, this can be an indication that the prior is over-fit, as we show
above (Table~\ref{tabModelChoiceEmpirical} and Figure~\ref{figPCA}).
Thus, interpreting such plots should be avoided, and the use of posterior
predictive analyses would be much more informative about the overall fit of
models.

\subsection*{The validity of \msb estimates}
\citet{Hickerson2013} claim that \citet{Oaks2012} ``assume that all previous
\msb results are invalid.''
With the exception of \citet{Hickerson2013}, we do not claim any previous
results of \msb are invalid.
Rather, we conservatively recommend that the common inference of temporally
clustered divergences
\citep{Barber2010, Bell2012, Carnaval2009, Chan2011, Daza2010, Hickerson2006,
    Huang2011, Lawson2010, Leache2007, Plouviez2009, Stone2012, Voje2009},
when not accompanied with the necessary simulation-based analyses to guide the
interpretation of such results, should be treated with caution, because the
method has been shown to spuriously infer clustered divergences over a range of
prior conditions.

\subsection*{Saturation of summary statistics}
\citet{Hickerson2013} claim that our priors ``cause much of the explored
parameter space to be beyond the threshold of saturation in most mtDNA genes.''
To explore this possibility, we simulated datasets under prior settings that
match two of the three priors used by \citet{Oaks2012}: $\meanDescendantTheta{}
\sim U(0.0005, 0.04)$ and $\ancestralTheta{} \sim U(0.0005, 0.02)$.
Under this prior, we draw divergence time parameters from a uniform
distribution of $U(0, 20)$, simulate datasets, and plot the \divt{} values
against the summary statistics calculated from the resulting datasets
(Figure~\ref{figSaturationPlot}).
Clearly, the priors used by \citet{Oaks2012} with upper limits on \divt{} of five
and 10 suffered from little to no effect from saturation.
Even at divergence times of 20 coalescent units, there is still signal in the
summary statistics used by \msb (Figure~\ref{figSaturationPlot}).
Thus, the assertion of \citet{Hickerson2013} does not apply to at least
two of the priors used by \citet{Oaks2012} and, as a result, does not
explain the bias they found.

\section*{Conclusions}
We demonstrate how the approximate Bayesian model choice method implemented in
\msb can be strongly biased away from models with greater parameter space.
As suggested by \citet{Oaks2012}, this is likely caused by the inappropriate
use of uniform priors on most of the model's parameters.
These priors necessitate the use of broad priors that place high prior density
in unlikely regions of parameter space, less the risk of excluding the truth
\emph{a priori}.
This likely reduces the marginal likelihoods of models with greater parameter
space, either due to more divergence time parameters or broader prior
distributions on those parameters.
We show that the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} does not mitigate this bias, but rather causes it to
manifest by sampling predominantly from models that may exclude the true values
of the parameters.
Exploring alternative prior probability distributions on most of the model's
parameters, in addition to different priors over divergence models, should
help mitigate the method's biases.

The work presented herein follows the principles of Open Notebook Science.
All aspects of the work were recorded in real-time via version-control
software and are publicly available at
\href{https://github.com/joaks1/msbayes-experiments}{https://github.com/joaks1/msbayes-experiments}.
All information necessary to reproduce our results are provided there.

>>>>

\section*{The potential implications of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected.''
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors to reflect the large amount of uncertainty about the
model's parameters (see their section ``Specifying and simulating the joint
prior'').
\citet{Oaks2012} further discuss how the use of uniform prior distributions in
\msb for many of the model's parameters necessitates awkward broad priors to
avoid excluding the truth, \textit{a priori}.
What \citet{Hickerson2013} mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world situations when a large amount of prior information is available. 
\citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

@@

%CWL:This should be in the section on model-averaging, not empirical Bayes
%limitations
We explored the propensity of the empirically informed model-averaging approach
of \citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a marginal posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

@@

\subsection*{Graphical prior comparisons}
\citet{Hickerson2013} advocate the use of what they call graphical checks of
prior models.
This entails generating a small number (1000) of random samples from the prior
and plotting the resulting summary statistics in comparison to the observed
statistics to see if they coincide (see Figure 1 of \citet{Hickerson2013}).
As we show above, this strategy can be misleading, because the resulting plots
of this approach have little correlation with the appropriateness of priors.
Given the richness of the \msb model ($\approx 600$ parameters for the Philippine
dataset analyzed by \citet{Hickerson2013}), we do not expect that 1000
\emph{random} draws from the vast prior parameter space will yield data and
summary statistics consistent with the observed data.
In fact, when such random draws are tightly clustered around the observed
statistics, this can be an indication that the prior is over-fit, as we show
above (Table~\ref{tabModelChoiceEmpirical} and Figure~\ref{figPCA}).
Thus, using such plots to select priors should be avoided, and the use of
posterior predictive analyses would be much more informative about the overall
fit of models.

\subsection*{Saturation of summary statistics}
\citet{Hickerson2013} claim the priors used by \citet{Oaks2012} ``cause much of
the explored parameter space to be beyond the threshold of saturation in most
mtDNA genes.'' To explore this possibility, we simulated datasets under prior
settings that match two of the three priors used by \citet{Oaks2012}:
$\meanDescendantTheta{} \sim U(0.0005, 0.04)$ and $\ancestralTheta{} \sim
U(0.0005, 0.02)$.
Under this prior, we draw divergence time parameters from a uniform
distribution of $U(0, 20)$, simulate datasets, and plot the \divt{} values
against the summary statistics calculated from the resulting datasets
(Figure~\ref{figSaturationPlot}).
Clearly, the priors used by \citet{Oaks2012} with upper limits on \divt{} of five
and 10 suffered from little to no effect from saturation.
Even at divergence times of 20 coalescent units, there is still signal in the
summary statistics used by \msb (Figure~\ref{figSaturationPlot}).
Thus, the assertion of \citet{Hickerson2013} does not apply to at least
two of the priors used by \citet{Oaks2012} and, as a result, does not
explain the bias they found.

\section*{Conclusions}
We demonstrate how the approximate Bayesian model choice method implemented in
\msb can be strongly biased away from models with greater parameter space.
As suggested by \citet{Oaks2012}, this is likely caused by the use of uniform
priors on most of the model's parameters.
Uniform distributions necessitate the use of broad priors that place high prior
density in unlikely regions of parameter space, less the risk of excluding the
truth \emph{a priori}.
This likely reduces the marginal likelihoods of models with greater parameter
space, either due to more divergence time parameters or broader prior
distributions on those parameters.
We show that the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} does not mitigate this bias, but rather causes it to
manifest by sampling predominantly from models that may exclude the true values
of the parameters.
Exploring alternative prior probability distributions on most of the model's
parameters, in addition to different priors over divergence models, should
help mitigate the method's biases.

Based on our results, we discourage the use of empirically informed uniform
priors in Bayesian model choice, especially when combined with model-averaging
\ldots

We do not ``assumed that all previous \msb results are invalid,'' as suggested
by \citet{Hickerson2013}.
Rather, we conservatively recommend that the common inference of temporally
clustered divergences \citep{Barber2010, Bell2012, Carnaval2009, Chan2011,
Daza2010, Hickerson2006, Huang2011, Lawson2010, Leache2007, Plouviez2009,
Stone2012, Voje2009}, when not accompanied with the necessary simulation-based
analyses to guide the interpretation of such results, should be treated with
caution, because the method has been shown to spuriously infer clustered
divergences over a range of prior conditions.

The work presented herein follows the principles of Open Notebook Science.
All aspects of the work were recorded in real-time via version-control
software and are publicly available at
\href{https://github.com/joaks1/msbayes-experiments}{https://github.com/joaks1/msbayes-experiments}.
All information necessary to reproduce our results is provided there.
